\documentclass[a4paper,11pt]{article}

\usepackage[left=0.6in,right=0.6in,top=0.6in,bottom=0.6in]{geometry}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}
\usepackage{fontenc}
\usepackage{inputenc}
\usepackage{xcolor}
\usepackage{tabularx}

% No colored links for ATS compatibility
\hypersetup{
  colorlinks=false,
  pdfborder={0 0 0}
}

% Section formatting: bold, uppercase, with full-width rule
\titleformat{\section}
  {\large\bfseries\uppercase}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{8pt}{4pt}

\setlist[itemize]{noitemsep, topsep=2pt, leftmargin=1.5em}

\pagestyle{empty}

\begin{document}

% ─── HEADER ───────────────────────────────────────────────────────────────────

\begin{center}
  {\LARGE \textbf{Aswin M Kumar}}\\[4pt]
  Thiruvananthapuram, Kerala, India\\[2pt]
  \href{mailto:aswin2k03.mk@gmail.com}{aswin2k03.mk@gmail.com}
  \;$|$\; +91 8590522637
  \;$|$\; \href{https://www.linkedin.com/in/aswinmkumar}{linkedin.com/in/aswinmkumar}
  \;$|$\; \href{https://github.com/aswin-m-kumar}{github.com/aswin-m-kumar}
  \;$|$\; \href{https://aswin-m-kumar.github.io}{aswin-m-kumar.github.io}
\end{center}

% ─── SUMMARY ──────────────────────────────────────────────────────────────────

\section{Summary}

Electrical and Electronics Engineering student at College of Engineering Trivandrum with hands-on experience in AI, IoT, embedded systems, and PCB design. Top 10 Finalist at Satwa25 National Hackathon (133 teams); recognized at Allianz Risk Consulting Compass-360 Expo for applied research in Li-ion battery fault detection. Proven track record of delivering end-to-end technical projects across hardware and software domains.

% ─── EDUCATION ────────────────────────────────────────────────────────────────

\section{Education}

\noindent
\textbf{Bachelor of Technology -- Electrical and Electronics Engineering} \hfill 2023 -- Present\\
College of Engineering Trivandrum, Kerala, India

\smallskip
\noindent\textit{Relevant Coursework:} Circuit Design, Embedded Systems, IoT Applications, Signal Processing, Control Systems

% ─── TECHNICAL SKILLS ─────────────────────────────────────────────────────────

\section{Technical Skills}

\noindent
\begin{tabular}{@{}ll}
\textbf{Programming Languages:} & Python, C, JavaScript, Flutter \\[2pt]
\textbf{Tools \& Platforms:}    & MATLAB, Simulink, Arduino, ESP32, KiCAD, SolidWorks, OpenCV, Git \\[2pt]
\textbf{Technical Areas:}       & Embedded Systems, PCB Design, IoT, Machine Learning, Computer Vision \\[2pt]
\textbf{Languages:}             & English (Fluent), Malayalam (Native), Hindi (Proficient) \\
\end{tabular}

% ─── EXPERIENCE ───────────────────────────────────────────────────────────────

\section{Experience}

\noindent
\textbf{Membership Coordinator \& Event Organizer} \hfill 2025 -- Present\\
\textit{SAEINDIA -- College of Engineering Trivandrum}
\begin{itemize}
  \item Coordinated SAEINDIA memberships for Herackles Racing CET and Zenith Motorsport CET; managed documentation and compliance for BAJA SAEINDIA 2026.
  \item Organized and conducted \textbf{CADClash}, a CAD design competition at Tech Rave (SAEINDIA CET Technical Fest); managed end-to-end event logistics and participant coordination.
  \item Organized \textbf{Biomimicry Competition}, a preliminary ideathon for a national-level SAE competition; facilitated concept pitching and evaluation rounds.
  \item Created and maintained 10+ Google Forms for event registrations and membership drives; tracked structured participant data in Excel sheets across SAEINDIA CET events.
\end{itemize}

\vspace{4pt}
\noindent
\textbf{Technical Team Member -- Suspension \& Steering} \hfill 2023 -- Present\\
\textit{EVolve Racing CET}
\begin{itemize}
  \item Engineered and optimized vehicle suspension and steering components using SolidWorks.
  \item Collaborated cross-functionally with the technical team to improve vehicle performance.
\end{itemize}

\vspace{4pt}
\noindent
\textbf{Trainee} \hfill 2024\\
\textit{Bosch Training Program}
\begin{itemize}
  \item Gained hands-on exposure to industrial automation, PLC systems, and control systems.
  \item Strengthened fundamentals of industrial machinery operation and maintenance.
\end{itemize}

\vspace{4pt}
\noindent
\textbf{Marketing \& Publicity Team Member} \hfill 2024\\
\textit{Dhwani24 -- College of Engineering Trivandrum}
\begin{itemize}
  \item Led outreach campaigns across multiple colleges, boosting event visibility and participation.
  \item Strengthened communication, coordination, and inter-college networking skills.
\end{itemize}

% ─── PROJECTS ─────────────────────────────────────────────────────────────────

\section{Projects}

\noindent
\textbf{Trash Nada -- AI-Powered Waste Management System} \hfill \href{https://github.com/aswin-m-kumar}{github.com/aswin-m-kumar}
\begin{itemize}
  \item Developed an AI-based waste classification and price prediction system using Python.
  \item Integrated IoT components for real-time monitoring and hotspot mapping of waste collection areas.
  \item Ranked \textbf{Top 10 among 133 teams} at the Satwa25 National Hackathon (36-hour competition).
\end{itemize}

\vspace{4pt}
\noindent
\textbf{Lithium Sense -- Early Fault Detection for Li-ion Batteries}
\begin{itemize}
  \item Researched early fault detection techniques for Li-ion batteries using temperature, voltage, and resistance indicators.
  \item Presented findings at the Allianz Risk Consulting Compass-360 Expo; received trophy and certificate.
\end{itemize}

\vspace{4pt}
\noindent
\textbf{Voice-Activated Smart Switch} \hfill \href{https://github.com/aswin-m-kumar}{github.com/aswin-m-kumar}
\begin{itemize}
  \item Developed a voice-controlled home automation switch using ESP32 and Python.
  \item Integrated real-time speech recognition for reliable device control.
\end{itemize}

\vspace{4pt}
\noindent
\textbf{Gesture-Controlled Game Interface} \hfill \href{https://github.com/aswin-m-kumar}{github.com/aswin-m-kumar}
\begin{itemize}
  \item Architected a gesture-based control system using Arduino and OpenCV for real-time hand detection.
  \item Enabled hands-free interactive gameplay through computer vision algorithms.
\end{itemize}

\vspace{4pt}
\noindent
\textbf{Browser-Based Mini Games Collection} \hfill \href{https://aswin-m-kumar.github.io}{aswin-m-kumar.github.io}
\begin{itemize}
  \item Developed multiple interactive browser games with HTML, CSS, and JavaScript.
  \item Authored game logic, event handling, and responsive UI; published on personal portfolio.
\end{itemize}

\vspace{4pt}
\noindent
\textbf{Optocoupler Circuit \& LM386 Audio Amplifier}
\begin{itemize}
  \item Assembled an optocoupler circuit for electrical signal isolation and noise reduction.
  \item Constructed an LM386-based audio amplifier circuit for low-power signal amplification.
\end{itemize}

\vspace{4pt}
\noindent
\textbf{Not\_KTU\_Results -- Satirical University Portal} \hfill \href{https://github.com/aswin-m-kumar/Not_KTU_Results}{GitHub} \;|\; \href{https://aswin-m-kumar.github.io/Not_KTU_Results/}{Live}
\begin{itemize}
  \item Launched a satirical university e-governance portal parody using HTML5, CSS3, JavaScript, Tailwind CSS, and Tone.js; deployed on GitHub Pages.
  \item Programmed a progressive multi-rule password game with real-time audio feedback (success chimes, error buzzes) using Tone.js.
  \item Crafted a responsive, mobile-first UI/UX with deliberate UX dark patterns simulating real portal failure states (504 timeout, delayed loading).
  \item Selected for \textbf{TinkerHub Useless Projects 2.0}; collaborated in a two-member team as lead for UI/UX design and content.
\end{itemize}

\vspace{4pt}
\noindent
\textbf{Portfolio Website} \hfill \href{https://aswin-m-kumar.github.io}{aswin-m-kumar.github.io}
\begin{itemize}
  \item Composed a personal portfolio using HTML, CSS, and JavaScript showcasing AI, IoT, and embedded systems projects.
\end{itemize}

% ─── ACHIEVEMENTS ─────────────────────────────────────────────────────────────

\section{Achievements}

\begin{itemize}
  \item \textbf{Top 10 Finalist} -- Satwa25 National Hackathon, Saintgits College of Engineering (133 competing teams, 2025).
  \item \textbf{Trophy \& Certificate} -- Allianz Risk Consulting Compass-360 Expo for research on \textit{Lithium Sense} (2025).
  \item \textbf{PCB Design Workshop} -- Completed workshop conducted by IET On Campus CET.
\end{itemize}

\end{document}
